Question 2: Is there a particular day of the week or hour of the day that inhabitants of high-rate neighbourhoods should be more wary of B&E’s? 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load the TPS break in data
break_and_enters <- read_csv("break_and_enters.csv")
glimpse(break_and_enters)
```

We want to get all of the high-frequency neighbourhoods, which we have definied as being in the top quartile of B&E occurances.

First, let's get a list of all unique neighbourhood values in break_and_enters$Neighbourhood, and their associated number of occurances.

```{r}
break_and_enters <- break_and_enters %>% filter(!is.na(Neighbourhood))
neighbourhoods <- table(break_and_enters$Neighbourhood)
neighbourhoods <- data.frame(neighbourhoods) 
colnames(neighbourhoods) <- c("Neighbourhood", "Frequency")
neighbourhoods <- neighbourhoods[order(neighbourhoods$Frequency, decreasing = TRUE),]  

print(neighbourhoods)
```

Now we get the top 25% of neighbourhoods with the most frequent B&E's.
```{r}
target_hoods <- head(neighbourhoods, 35)
print(target_hoods)
```

Finally, we can grab a subset of all rows in our raw break_and_enters dataframe, and target rows that are in one of those 35 neighbourhoods.

```{r}
break_and_enters <- break_and_enters %>% 
  mutate(targeted = ifelse(Neighbourhood %in% target_hoods$Neighbourhood, "Bottom 25%", "Top 75%"))
  
print(break_and_enters)

```

Now let's graph out a frequency table of B&E's per day.
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrenceyear))

ggplot(targeted, aes(x = occurrenceyear)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Year") +
  ylab("Number of Occurrences")
```
We can only assume that there is little data recorded in this database on B&E's before 2014. Broadly speaking, we have recently seen an increasing trend year on year, with 2019 being the highest on record.

Here's another one based on month:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrencemonth))

ggplot(targeted, aes(x = occurrencemonth)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Month") +
  ylab("Number of Occurrences") +
  scale_x_discrete(label = month.name)
  
```

One for occurence day:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrenceday))

ggplot(targeted, aes(x = occurrenceday)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Day of the Month") +
  ylab("Number of Occurrences")
```

On occurrence day of the week:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrencedayofweek))

day.name <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

ggplot(targeted, aes(x = occurrencedayofweek)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Day of the Week") +
  ylab("Number of Occurrences") +
  scale_x_discrete(label = day.name)
```

And finally, occurence hour:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrencehour))

ggplot(targeted, aes(x = occurrencehour)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Hour of the Day") +
  ylab("Number of Occurrences")
```

All this being said, since all these trends are looking very similar for both groups, we put up the question: are there any differences between the bottom 25% and the top 75% in the timing of B&Es?

Null Hypothesis: There is no difference in the patterns describing when B&Es occur in our worst-affected neighbourhoods.
Alternative Hypothesis: The patterns describing when B&Es occur are different in our worst-affected neighbourhoods.

We do this by calculating the absolute difference between the number of occurences per time period in our bottom 75% data and our top 25% sample. First let's create seperate dataframes for occurrence in the top 25% and bottom 75%.
```{r}
top25 <- break_and_enters %>%
  filter(Neighbourhood %in% target_hoods$Neighbourhood)

bottom75 <- break_and_enters %>%
  filter(!Neighbourhood %in% target_hoods$Neighbourhood)

diff_factor = nrow(bottom75) / nrow(top25) 
```

Then let's establish our test statistic. We are using the sum of the differences in month-on-month changes between our two groups of B&Es. The lower this number is, the lesser the differences are in changes between our two groups, and thus our trends must be similar. Conversely, the higher this number is, the more divergent our two trends are.
```{r}
table25 <- table(top25$occurrencemonth)
table25 <- data.frame(table25)
table25 <- table25[order(match(table25$Var1, month.name)), ] %>%
  mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)

table75 <- table(bottom75$occurrencemonth)
table75 <- data.frame(table75)
table75 <- table75[order(match(table75$Var1, month.name)), ] %>%
  mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)

delta <- abs(table75$change - table25$change)
delta <- tibble(delta)
delta <- delta %>% filter(!is.na(delta))

test_stat <- sum(delta)
print(test_stat)
```

Next we run a simulation by drawing random B&Es and looking at their month-on-month change trends. 
```{r}
repetitions <- 1000; # number of repetitions (i.e. possible groupings)
simulated_values <- rep(NA, repetitions); # empty vector for sim. values

for(i in 1:repetitions){
  
  simdata <- sample_n(break_and_enters, 21142, replace = TRUE)
  simdata <- table(simdata$occurrencemonth)
  simdata <- data.frame(simdata)
  simdata <- simdata[order(match(simdata$Var1, month.name)), ] %>%
    mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)
  
  delta <- abs(table75$change - simdata$change)
  delta <- tibble(delta)
  delta <- delta %>% filter(!is.na(delta))
  simulated_values[i] <- sum(delta)

}

simulated_values <- tibble(value = simulated_values)
median <- median(simulated_values$value)
  
simulated_values %>% ggplot(aes(x=value)) +  
  geom_histogram(colour = "black", fill = "grey") +  
  geom_vline(xintercept = median  - abs(median - test_stat), color = "red") +  
  geom_vline(xintercept = median + abs(median - test_stat), color = "blue")

pvalue <- simulated_values %>%  
  filter(abs(value - median) >= abs(test_stat - median)) %>%  
  summarise(p_value = n() / repetitions)
print(pvalue)
```
We get a p-value of 0.022, suggesting moderate evidence against the null hypothesis. In other words, there is evidence to suggest that the monthly trend of B&Es differs between high-risk neighbourhoods and low-risk ones.

Again, let's do the same but for occurrence hour.
```{r}
table25 <- table(top25$occurrencehour)
table25 <- data.frame(table25)
table25 <- table25[order(match(table25$Var1, month.name)), ] %>%
  mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)

table75 <- table(bottom75$occurrencehour)
table75 <- data.frame(table75)
table75 <- table75[order(match(table75$Var1, month.name)), ] %>%
  mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)

delta <- abs(table75$change - table25$change)
delta <- tibble(delta)
delta <- delta %>% filter(!is.na(delta))

test_stat <- sum(delta)
print(test_stat)

repetitions <- 1000; # number of repetitions (i.e. possible groupings)
simulated_values <- rep(NA, repetitions); # empty vector for sim. values

for(i in 1:repetitions){
  
  simdata <- sample_n(break_and_enters, 21142, replace = TRUE)
  simdata <- table(simdata$occurrencehour)
  simdata <- data.frame(simdata)
  simdata <- simdata[order(match(simdata$Var1, month.name)), ] %>%
    mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)
  
  delta <- abs(table75$change - simdata$change)
  delta <- tibble(delta)
  delta <- delta %>% filter(!is.na(delta))
  simulated_values[i] <- sum(delta)

}

simulated_values <- tibble(value = simulated_values)
median <- median(simulated_values$value)
  
simulated_values %>% ggplot(aes(x=value)) +  
  geom_histogram(colour = "black", fill = "grey") +  
  geom_vline(xintercept = median  - abs(median - test_stat), color = "red") +  
  geom_vline(xintercept = median + abs(median - test_stat), color = "blue")

pvalue <- simulated_values %>%  
  filter(abs(value - median) >= abs(test_stat - median)) %>%  
  summarise(p_value = n() / repetitions)
print(pvalue)
```
This time we get a p-value of 0, suggesting that there is very strong evidence against the null hypothesis. In other words.

And one more time for day of the week.
```{r}
table25 <- table(top25$occurrencedayofweek)
table25 <- data.frame(table25)
table25 <- table25[order(match(table25$Var1, month.name)), ] %>%
  mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)

table75 <- table(bottom75$occurrencedayofweek)
table75 <- data.frame(table75)
table75 <- table75[order(match(table75$Var1, month.name)), ] %>%
  mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)

delta <- abs(table75$change - table25$change)
delta <- tibble(delta)
delta <- delta %>% filter(!is.na(delta))

test_stat <- sum(delta)
print(test_stat)

repetitions <- 1000; # number of repetitions (i.e. possible groupings)
simulated_values <- rep(NA, repetitions); # empty vector for sim. values

for(i in 1:repetitions){
  
  simdata <- sample_n(break_and_enters, 21142, replace = TRUE)
  simdata <- table(simdata$occurrencedayofweek)
  simdata <- data.frame(simdata)
  simdata <- simdata[order(match(simdata$Var1, month.name)), ] %>%
    mutate(change = (Freq - lag(Freq)) / lag(Freq) * 100)
  
  delta <- abs(table75$change - simdata$change)
  delta <- tibble(delta)
  delta <- delta %>% filter(!is.na(delta))
  simulated_values[i] <- sum(delta)

}

simulated_values <- tibble(value = simulated_values)
median <- median(simulated_values$value)
  
simulated_values %>% ggplot(aes(x=value)) +  
  geom_histogram(colour = "black", fill = "grey") +  
  geom_vline(xintercept = median  - abs(median - test_stat), color = "red") +  
  geom_vline(xintercept = median + abs(median - test_stat), color = "blue")

pvalue <- simulated_values %>%  
  filter(abs(value - median) >= abs(test_stat - median)) %>%  
  summarise(p_value = n() / repetitions)
print(pvalue)
```



























