Question 2: Is there a particular day of the week or hour of the day that inhabitants of high-rate neighbourhoods should be more wary of B&E’s? 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load the TPS break in data
break_and_enters <- read_csv("break_and_enters.csv")
glimpse(break_and_enters)
```

We want to get all of the high-frequency neighbourhoods, which we have definied as being in the top quartile of B&E occurances.

First, let's get a list of all unique neighbourhood values in break_and_enters$Neighbourhood, and their associated number of occurances.

```{r}
break_and_enters <- break_and_enters %>% filter(!is.na(Neighbourhood))
neighbourhoods <- table(break_and_enters$Neighbourhood)
neighbourhoods <- data.frame(neighbourhoods) 
colnames(neighbourhoods) <- c("Neighbourhood", "Frequency")
neighbourhoods <- neighbourhoods[order(neighbourhoods$Frequency, decreasing = TRUE),]  

print(neighbourhoods)
```

Now we get the top 25% of neighbourhoods with the most frequent B&E's.
```{r}
target_hoods <- head(neighbourhoods, 35)
print(target_hoods)
```

Finally, we can grab a subset of all rows in our raw break_and_enters dataframe, and target rows that are in one of those 35 neighbourhoods.

```{r}
break_and_enters <- break_and_enters %>% 
  mutate(targeted = ifelse(Neighbourhood %in% target_hoods$Neighbourhood, "Bottom 25%", "Top 75%"))
  
print(break_and_enters)

```

Now let's graph out a frequency table of B&E's per day.
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrenceyear))

ggplot(targeted, aes(x = occurrenceyear)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Year") +
  ylab("Number of Occurrences")
```
We can only assume that there is little data recorded in this database on B&E's before 2014. Broadly speaking, we have recently seen an increasing trend year on year, with 2019 being the highest on record.

Here's another one based on month:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrencemonth))

ggplot(targeted, aes(x = occurrencemonth)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Month") +
  ylab("Number of Occurrences") +
  scale_x_discrete(label = month.name)
  
```

One for occurence day:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrenceday))

ggplot(targeted, aes(x = occurrenceday)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Day of the Month") +
  ylab("Number of Occurrences")
```

On occurrence day of the week:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrencedayofweek))

day.name <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

ggplot(targeted, aes(x = occurrencedayofweek)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Day of the Week") +
  ylab("Number of Occurrences") +
  scale_x_discrete(label = day.name)
```

And finally, occurence hour:
```{r}
targeted <- break_and_enters %>% 
  group_by(targeted) %>% 
  filter(!is.na(occurrencehour))

ggplot(targeted, aes(x = occurrencehour)) +
  geom_bar(colour = "black", fill = "blue", alpha = 0.2) +
  facet_wrap(~targeted) +
  xlab("Hour of the Day") +
  ylab("Number of Occurrences")
```

All this being said, since all these trends are looking very similar for both groups, we put up the question: are there any differences between the bottom 25% and the top 75% in the timing of B&Es?

Null Hypothesis: There is no difference in the patterns describing when B&Es occur in our worst-affected neighbourhoods.
Alternative Hypothesis: The patterns describing when B&Es occur are different in our worst-affected neighbourhoods.







