Question 2: Is there a particular day of the week or hour of the day that inhabitants of high-rate neighbourhoods should be more wary of B&E’s? 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load the TPS break in data
break_and_enters <- read_csv("break_and_enters.csv")
glimpse(break_and_enters)
```

We want to get all of the high-frequency neighbourhoods, which we have definied as being in the top quartile of B&E occurances.

First, let's get a list of all unique neighbourhood values in break_and_enters$Neighbourhood, and their associated number of occurances.

```{r}
neighbourhoods <- table(break_and_enters$Neighbourhood)
neighbourhoods <- data.frame(neighbourhoods) 
colnames(neighbourhoods) <- c("Neighbourhood", "Frequency")
neighbourhoods <- neighbourhoods[order(neighbourhoods$Frequency, decreasing = TRUE),]  

print(neighbourhoods)
```

Now we get the top 25% of neighbourhoods with the most frequent B&E's.
```{r}
target_hoods <- head(neighbourhoods, 35)
print(target_hoods)
```

Finally, we can grab a subset of all rows in our raw break_and_enters dataframe, and target rows that are in one of those 35 neighbourhoods.

```{r}
target_data <- break_and_enters %>%
      filter(Neighbourhood %in% target_hoods$Neighbourhood)

print(target_data)
```

Now let's graph out a frequency table of B&E's per day
```{r}

```

TODO:
  -Daily graphs, hourly graphs
  -Comparison with B&E frequencies of every other neighbourhood
  -Some sort of written analysis






