
Is there a certain kind of B&E that occurs more often in these high-rate neighborhoods?

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load the TPS break in data
break_and_enters <- read_csv("break_and_enters.csv")
```

#create a new variable that represents the proportion of all reported B&E's that occurred in this neighbourhood.
```{r}
grouped_hood <- break_and_enters %>% 
  filter(!is.na(Neighbourhood)) %>%
  group_by(Neighbourhood) %>%
  mutate(number = n()) %>%
  mutate(prop = number/43302)
break_and_enters_prop <- merge(break_and_enters,grouped_hood,by=c("X1", "Index", "event_unique_id", "occurrencedate", "reporteddate", "premisetype", "offence", "reportedyear", "reportedmonth", "reportedday", "reporteddayofyear", "reporteddayofweek", "reportedhour", "occurrenceyear", "occurrencemonth", "occurrenceday", "occurrencedayofyear", "occurrencedayofweek", "occurrencehour", "MCI", "Division", "Hood_ID", "Long", "Lat"))
```
 
```{r}
ggplot(break_and_enters_prop,
aes(x = "", y=prop)) +
geom_boxplot()
break_and_enters_prop %>%
summarise(n=n(),
Q1=quantile(prop, 0.25),
med=median(prop),
mean=mean(prop),
Q3=quantile(prop, 0.75),
max=max(prop))
```

```{r}
b_and_e_top <- break_and_enters_prop %>%
  filter(prop >= 0.01457208)
b_and_e_lower <- break_and_enters_prop %>%
  filter(prop <= 0.005565563)
b_and_e_extremes <- rbind(b_and_e_top, b_and_e_lower)
b_and_e_extremes <- b_and_e_extremes %>% mutate(level = ifelse(prop >= 0.01457208, "high", "low"))

```

First, we try to identify which type of B&E occurs the most often in high-rate neighborhoods. To do this, we use a simple bar graph.
```{r}
ggplot(b_and_e_top, aes(x = offence)) +
  geom_bar(color="darksalmon", fill="coral") + labs(x = "B&E Offence Type", y = "Number of Occurrences")
```

As we can see from this graph, B&E is the most common offence type in neighborhoods with high rates.

Next, we want to see if this trend is different from that of the low-rate neighborhoods. This can be done through a hypothesis test. 
Our hypothesis test will seek to 
$H_0$: $P_\text{diff}$ = 0
$H_a$: $P_\text{diff}$ != 0
where $H_0$ represents the null hypothesis, $H_a$ the alternative hypothesis, and $P_\text{diff}$ the difference between the proportion of a certain offence type in high B&E rate neighborhoods and that of low B&E rate neighborhoods.

```{r}
prop_bande <- b_and_e_extremes %>% 
  group_by(level) %>%
  summarise(n = n(), num_bne = sum(offence == "B&E"), prop_bne = num_bne/n)
test_stat <- prop_bande %>%
  summarise(test_stat = diff(prop_bne))
test_stat
```

```{r}
set.seed(123)
repetitions <- 1000
simulated_differences <- rep(NA, times=repetitions)
for(i in 1:repetitions){
  simdata <- b_and_e_extremes %>%
    mutate(level=sample(level)) %>%
    group_by(level) %>%
    summarise(n = n(), num_bne = sum(offence == "B&E"), prop_bne = num_bne/n)
  sim_prop_diff <- simdata %>% summarise(value = diff(prop_bne))
  simulated_differences[i] <- as.numeric(sim_prop_diff)
}
sim <- tibble(prop_diff = simulated_differences)
```

```{r}
ggplot(sim, aes(x=prop_diff)) +
geom_histogram(binwidth = 0.005, fill="gray", color="black") +
labs(x = "Difference in proportion of B&E (offence) for neighborhoods 
     with high B&E rates versus those with low B&E rates") + 
  geom_vline(xintercept=c(test_stat, -test_stat), color="red")
sim %>% 
  filter(prop_diff >= abs(test_stat) | prop_diff <= -abs(test_stat))%>%
  summarise(pvalue = n() / repetitions)
```
Since the p-value is less than 0.0001, we have strong evidence against the null hypothesis that there is no difference in proportion of B&E offences between neighborhoods with high B&E rates and those with low B&E rates.

```{r}
b_and_e_extremes <- b_and_e_extremes %>% 
  mutate(BnE = ifelse(premisetype == "B&E", "Yes", "No")) 
ggplot(b_and_e_extremes, aes(x=BnE, y=prop)) +
  geom_boxplot() + theme_bw() + facet_wrap(~level)
summary(lm(number ~ BnE, data=b_and_e_top))$coefficients
```

