---
output:
  pdf_document: default
  html_document: default
---

<<<<<<< HEAD
What, if any, is the most common type of Break and Enters (B&E) that occur in high-rate B&E neighbouroods, and does this type occur more often than in low-rate B&E neighbourhoods?


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load the TPS break in data
break_and_enters <- read_csv("break_and_enters.csv")
```

#create a new variable that represents the proportion of all reported B&E's that occurred in this neighbourhood.
```{r}
grouped_hood <- break_and_enters %>% 
  filter(!is.na(Neighbourhood)) %>%
  group_by(Neighbourhood) %>%
  mutate(number = n()) %>%
  mutate(prop = number/43302)
break_and_enters_prop <- merge(break_and_enters,grouped_hood,by=c("X1", "Index", "event_unique_id", "occurrencedate", "reporteddate", "premisetype", "offence", "reportedyear", "reportedmonth", "reportedday", "reporteddayofyear", "reporteddayofweek", "reportedhour", "occurrenceyear", "occurrencemonth", "occurrenceday", "occurrencedayofyear", "occurrencedayofweek", "occurrencehour", "MCI", "Division", "Hood_ID", "Long", "Lat"))
```
 
```{r}
ggplot(break_and_enters_prop,
aes(x = "", y=prop)) +
geom_boxplot()
break_and_enters_prop %>%
summarise(n=n(),
Q1=quantile(prop, 0.25),
med=median(prop),
mean=mean(prop),
Q3=quantile(prop, 0.75),
max=max(prop))
```

```{r}
b_and_e_top <- break_and_enters_prop %>%
  filter(prop >= 0.01457208)
b_and_e_lower <- break_and_enters_prop %>%
  filter(prop <= 0.005565563)
b_and_e_extremes <- rbind(b_and_e_top, b_and_e_lower)
b_and_e_extremes <- b_and_e_extremes %>% mutate(level = ifelse(prop >= 0.01457208, "high", "low"))

```

First, we try to identify which type of B&E occurs the most often in high-rate neighborhoods. To do this, we use a simple bar graph.
```{r}
ggplot(b_and_e_top, aes(x = offence)) +
  geom_bar(color="darksalmon", fill="coral") + 
  labs(x = "B&E Offence Type", y = "Number of Occurrences") +
  coord_flip() +
  ggtitle("Frecuency of Each Type of Offence in 
          High-Rate Neighborhoods")
```

As we can see from this graph, B&E is the most common offence type in neighborhoods with high rates.

Next, we want to see if this trend is different from that of the low-rate neighborhoods. To study the relationship between proportion of specifically B&E offences and general B&E rate in neighborhoods, we will conduct a hypothesis test.
$H_0$: $P_\text{diff}$ = 0
$H_a$: $P_\text{diff}$ != 0
where $H_0$ represents the null hypothesis, $H_a$ the alternative hypothesis, and $P_\text{diff}$ the difference between the proportion of a certain offence type in high B&E rate neighborhoods and that of low B&E rate neighborhoods.

```{r}
prop_bande <- b_and_e_extremes %>% 
  group_by(level) %>%
  summarise(n = n(), num_bne = sum(offence == "B&E"), prop_bne = num_bne/n)
test_stat <- prop_bande %>%
  summarise(test_stat = diff(prop_bne))
test_stat
```

```{r}
set.seed(123)
repetitions <- 1000
simulated_differences <- rep(NA, times=repetitions)
for(i in 1:repetitions){
  simdata <- b_and_e_extremes %>%
    mutate(level=sample(level)) %>%
    group_by(level) %>%
    summarise(n = n(), num_bne = sum(offence == "B&E"), prop_bne = num_bne/n)
  sim_prop_diff <- simdata %>% summarise(value = diff(prop_bne))
  simulated_differences[i] <- as.numeric(sim_prop_diff)
}
sim <- tibble(prop_diff = simulated_differences)
```

```{r}
#ggplot(sim, aes(x=prop_diff)) +
#geom_histogram(binwidth = 0.005, fill="gray", color="black") +
#labs(x = "Difference in proportion of B&E (offence) for neighborhoods 
   #  with high B&E rates versus those with low B&E rates") + 
 # geom_vline(xintercept=c(test_stat, -test_stat), color="red")
sim %>% 
  filter(prop_diff >= abs(test_stat) | prop_diff <= -abspr(test_stat))%>%
  summarise(pvalue = n() / repetitions)
```
Since the p-value is less than 0.0001, we have very strong evidence against the null hypothesis that there is no difference in proportion of B&E offences between neighborhoods with high B&E rates and those with low B&E rates. Thus we can conclude that there is a difference in proportion of the B&E type offences between high and low rate B&E rate neighbourhoods. 

Next we will show how the proportion of Break and Enters differs between high and low rate neighbourhoods on a plot: 
```{r}
ggplot(b_and_e_extremes, aes(x=level, y=prop)) +
  geom_boxplot() + theme_bw()
```
From the high rate neighbourhoods it is evident ...


*change this description for multilinear regression
Further, we will use another method - linear regresssion model to predict the proportion of BnE using the BnE as a predictor. The regression equation will be: 
BnEprop$_{i}$=$\beta _{0}$+$\beta _{1}$I 
Where our dependent variable is BnEprop for the ith observation, I is the independent variable, $\beta B_{0}$ is the intercept parameter and $\beta B_{1}$ is the slope parameter.
We are interested to test the
$H_0$: $P_\text{diff}$ = 0
$H_a$: $P_\text{diff}$ != 0
where $H_0$ represents the null hypothesis, $H_a$ the alternative hypothesis, and $P_\text{diff}$ is difference between the proportion of a certain offence type in high B&E rate neighborhoods and that of low B&E rate neighborhoods.
We will assess whether there is a linear association between the two variables.  
```{r}
parallel_lines <- lm(prop ~ offence + level, data = b_and_e_extremes)
summary(parallel_lines)$coefficients
library(broom) 
augment(parallel_lines)
b_and_e_extremes %>% ggplot(aes(x=offence, y=prop, color=level))+geom_point(alpha=0.5) + geom_line(data=augment(parallel_lines), aes(y=.fitted, colour=level), lwd=1.5) 

```

From the model, we can see that the p-value is 

<<<<<<< HEAD

=======
>>>>>>> 09d98f4bdb7dcd8b96e2980566b3dc32811776bb
